Stack Safety as a Security Property

### 2020-07-06 main.tex
Comment squashing

\bcp{ Comments on the example:
\begin{itemize}
\item We will also need to be careful about fonts ($f$ vs {\texttt f}),
capitalization of register names (sp vs SP), etc. Maybe typeset instructions
in small caps?  Maybe typeset everything that is part of a concrete machine
in small caps??
%
\item The colors are helpful in making the big page of instruction traces easier
on the eye; maybe they would be even more helpful if
corresponding colors appeared elsewhere in the example (on the instructions
themselves, e.g.).  But we need to be careful to keep it readable -- maybe
they should be background colors, like you've done, rather than text colors.
\item Asking readers to wade through all this is asking quite a bit!  We
need to make sure we are going to get sufficient value out of the example
later (I think we can, but we should really convince ourselves) to make it
worthwhile.
\item Create a new column that just literally pronounces each instruction in
English, so people don't have to read RISC-V opcodes.
\item As discussed, we should move this to before section 2, we should
extend it with a bit more at the end so we can talk about the lazy policy
with the same example, we should add
in some bad variants (doing it here replaces the ``Examples'' from the
Discussion section), and we should consider discussing the attacker model
here (we need to discuss it someplace in any case!)
\end{itemize}
}

@@

Mapping a conventional architecture to this abstract interface is
straightforward. For the running example of the previous section,
$\WORDS$ is the set of 64-bit integers, $\REGS$ is the set $\{r_0,
\cdots, r_{31}\} \cup \{\PCname\}$, and $\SP = r_2$. Observations are
the writes to the special $\rout$ location: if during an execution
step a word $w$ is written to $\rout$ then $\obs = w$, otherwise $\obs
= \tau$.

\leo{Other choices for observations? Where should that be discussed?}
\bcp{But in this paragraph we are describing the particular
choise that we make for our running example, no?  But we certainly want to
discuss this fully someplace!}

@@

\bcp{I'm getting a little lost in
  all these.  E.g., do these traces include the final state of a finite
  execution?  If so, what observation is it paired with?}\leo{The final
  observation is a $\tau$ based on the rule in the inlined figure, so
  it is essentially ignored. Point that out somehow?}\sna{It is now pointed
  out, but it also reminds me as we go back to prefix-up-to that the final
  observation of a prefix needs to be tau...}

\paragraph*{Until}
The ``Until'' operation \(\PUT(\Trace,f)\) \bcp{Wouldn't
``While'' be more mnemonic?} \sna{Appealing, but it's more of a
``while-not''? Trying out ``until''. In any case... moving away
from doing joins means this needs to get some work to eliminate
the trailing observation. Here's an attempt.} takes a trace
\(\Trace : \mathit{trace} \TRACEELEMS \times \OBSS\) and a predicate
on elements \(f \subset \TRACEELEMS\) and gives the prefix of
\(\Trace\) ending with the first element on which \(f\) holds.
Subtly, because the observation associated with a trace represents its
next step, when we take a prefix from a trace containing observations
we must replace the final observation with a \(\tau\).

@@

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
Let \(f\) be a predicate on machine states. Then we define \(\mach
\hookrightarrow \machOT | f\) (read ``\(\machOT\) is the prefix of
running \(\mach\) up to \(f\)''): \bcp{M and M' should be swapped, I
  think.}  \leo{There were inconsistencies which i fixed. I wanted the
  metavariables defined to be consistent and the ``temporary''
  variable which is the full trace to be primed. Should I swap those?}

>>>>

@@

\leo{Other choices for observations? Where should that be discussed?}
\bcp{But in this paragraph we are describing the particular
choise that we make for our running example, no?  But we certainly want to
discuss this fully someplace!}
\leo{Here: Many observation choices. Next: Simplify:}
Mapping a conventional architecture to this abstract interface is
straightforward. For the running example of the previous section,
$\WORDS$ is the set of 64-bit integers, $\REGS$ is the set $\{r_0,
\cdots, r_{31}\} \cup \{\PCname\}$, and $\SP = r_2$. Observations are
the writes to the special $\rout$ location: if during an execution
step a word $w$ is written to $\rout$ then $\obs = w$, otherwise $\obs
= \tau$.

@@

\paragraph*{Until}
The ``Until'' operation \(\PUT(\Trace,f)\)
%\bcp{Wouldn't
%``While'' be more mnemonic?} \sna{Appealing, but it's more of a
%``while-not''? Trying out ``until''. In any case... moving away
%from doing joins means this needs to get some work to eliminate
%the trailing observation. Here's an attempt.}
takes a trace
\(\Trace : \mathit{trace} \TRACEELEMS \times \OBSS\) and a predicate
on elements \(f \subset \TRACEELEMS\) and gives the prefix of
\(\Trace\) ending with the first element on which \(f\) holds.
Subtly, because the observation associated with a trace represents its
next step, when we take a prefix from a trace containing observations
we must replace the final observation with a \(\tau\).

@@

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
Let \(f\) be a predicate on machine states. Then we define \(\mach
\hookrightarrow \machOT | f\) (read ``\(\machOT\) is the prefix of
running \(\mach\) up to \(f\)''):
